```{r setup, echo=FALSE}
library(knitr)
opts_chunk$set(tidy=TRUE, highlight=T, figalign="center",
 fig.height=6, fig.width=6, message=F, error=F, warning=F)
```


```{r}
data<-read.table("stats",skip=1)
data$V2<-as.character(data$V2)
data$V4<-as.character(data$V4)
data$V5<-data$V5/abs(data$V5)
data$V5[data$V5==1]<-"Add"
data$V5[data$V5==-1]<-"Na"
data$V6<-data$V6/abs(data$V6)
data$V6[data$V6==1]<-"Mut"
data$V6[data$V6==-1]<-"Na"
data$changes<-paste(data$V5,data$V6)
data$TP<-apply(data[,c(2,4)],1,function(x){
  v<-grep(x[1],x[2],ignore.case=T)
  if (length(v)==0){v<-0}
  return (v)
})
```


Proportion of mapped and no-mapped sequences
```{r dev='svg'}
library(ggplot2)
ggplot(data,aes(V8,fill=V3))+
  geom_bar()+
  theme_bw()+ labs(x="")+
  scale_fill_brewer("mapped",palette="Set1")
```

How size affects the alignments
```{r dev='svg'}
ggplot(data,aes(V8,V7,fill=V3))+
  geom_boxplot()+
  theme_bw()+ labs(x="")+
  scale_fill_brewer("mapped",palette="Set1")
```

How changes affect the alignment
```{r dev='svg',fig.width=9}
ggplot(data,aes(V8,fill=changes))+
  geom_bar()+
  theme_bw()+ labs(x="")+
  facet_wrap(~V3)+
  scale_fill_brewer("changes",palette="Set1")
```


How many were assigned to only the correct miRNA. Normally miRNA can map to other miRNAs that are from the same family. "Red" will be sequences mapping to multiple miRNAs.
```{r dev='svg'}
ggplot(data[data$V3=="yes",],aes(V8,fill=factor(TP)))+
  geom_bar()+
  theme_bw()+ labs(x="")+
  scale_fill_brewer("correct",palette="Set1")
```


# isomirs

```{r load-iso}
stat_iso <- read.table("isomirs_stats.tsv")
```

```{r uniquely}
uniquely = subset(stat_iso, V8 == 1)
multi = subset(stat_iso, V8 > 1)
```

Number of sequences with multihits `r length(unique(multi[,1]))` and 
uniquelye mapped `r nrow(uniquely)`.

```{r correct}
uniquely$dif5 <- uniquely$V6 - uniquely$V4
```
